Geodesic Flow on the Necker Cube Surface

### 2017-08-01 paper.tex
lastminute

\begin{figure}[H]
\includegraphics[width=3in]{homologyclass.png}
\centering
\end{figure}
Every curve intersects two others. By constructing a $12\times12$ matrix where the rows represent each curve and the columns represent their intersections with other curves, we can see that the rank of said matrix is 10. This is to be expected as the genus of $\mathbf M$ is 5. From these curves we construct homology classes $u,v,$ and $z$. $u$ and $v$ are the curves that were the outermost edges of the tori in $\mathbf{M}$'s original representation (Figure $\ref{fig:mtilda}$). We can see from Figure $\ref{fig:utilda}$ that crossing over one of these edges corresponds to a shift of the even integer index pair that determines exactly which of the square shaped holes a point on the surface is near to. The $z$ class of cylinder curves lie on the cylinders that take a path from one plane to the next in our cover. Since one plane is related to exactly two others, it is impossible to go from the first to the third, or the second to the fourth, and vice versa.

Regardless, $u$ and $v$ are the most important homology classes that we use to determine whether or not a path properly closes on the four-fold cover. Let $\alpha:[0,1]\rightarrow\mathbf M$ be a curve on the surface such that $\alpha(0)=\alpha(1)=x_0\in\mathbf{M}$. Take $f:\tilde{\mathbf U}\rightarrow\mathbf M$ to be the covering map that takes every point on $\tilde{\mathbf U}$ to its quotient in $\mathbf{M}$. We will fix a point $\tilde{x}_0\in\tilde{\mathbf U}$ such that the lifted path $\tilde\alpha(0)=\tilde{x}_0$ under the function $f$. $\alpha$ is a closed path in $\pi_1(\mathbf M,x_0)$. We denoted the class of paths $\alpha$ as [$\alpha$]$\in H_1(\tilde{\mathbf{M}},\mathbb Z)$, and define the function,

\begin{align}
i:H_1(\mathbf{M},\mathbb Z)\times H_1(\mathbf{M},\mathbb Z)\rightarrow \mathbb Z,
\end{align}
to return the intersection number of two homology classes. Out of convention, we consider a positive intersection to adhere to the right-hand rule and take the crossings to be relative to $u$ and $v$. With that being said, the signed homology classes of gamma curves are

@@

The $\mathbb{Z}^2$ cover, $\tilde{\mathbf{U}}$, is associated to the kernel of the homomorphism
\begin{align}
\Omega_{u,v}:\pi_1(\mathbf{M},x_0)\rightarrow \mathbb{Z}^2, \text{ such that } \alpha\mapsto(i(u,[\alpha]),i(v,[\alpha])).
\end{align}
Suppose that $h:\mathbf{M}\rightarrow\mathbf{M}$ is an automorphism of the surface such that dir $h\in SL(\mathbf M)$. $h$ induces the isomorphism, $h_*:\pi_1(\mathbf{M},x_0)\rightarrow \pi_1(\mathbf{M},x_0)$. Likewise, $f$ induces the inclusion map $f_*:\pi_1(\tilde{\mathbf{U}},\tilde x_0)\hookrightarrow\pi_1(\mathbf{M},x_0)$. If $\pi_1(\tilde{\mathbf{U}},\tilde x_0) = $ Ker $\Omega_{u,v}$, then it must be true that the kernel of such a homomorphism is preserved under $h_*$.

The actions of $h_*$ are dual to the actions of dir $h$, denoted $h'$, on the sets of odd-odd and even-odd $\mathbb{Z}^2$ vectors, $\mathcal{O}$ and $\mathcal{E}$. In particular, the action of $\mathbb X$ on $\mathcal{O}$ and $\mathcal{E}$ is self-contained and well-defined. This is vital as what we want to show is that $h'(\alpha')$, such that $\alpha'$ is a constant, is dual to $h_*([\alpha])$. In which case, it should also be true that $h_*(\alpha)\mapsto(i(u,h_*([\alpha])),i(v,h_*([\alpha])))$, under $i$. And since intersection number is a non-degenerate bilinear form,

>>>>

\begin{figure}[H]
\includegraphics[width=3in]{homologyclass.png}
\centering
\end{figure}
Every curve intersects two others. By constructing a $12\times12$ matrix where the rows represent each curve and the columns represent their intersections with other curves, we can see that the rank of said matrix is 10. This is to be expected as the genus of $\mathbf M$ is 5. From these curves we construct homology classes $u,v,$ and $z$. $u$ and $v$ are the curves that were the outermost edges of the tori in $\mathbf{M}$'s original representation (Figure $\ref{fig:mtilda}$). We can see from Figure $\ref{fig:utilda}$ that crossing over one of these edges corresponds to a shift of the even integer index pair that determines exactly which of the quotients of $\tilde{\mathbf{U}}$ a terminal point of a lifted path on the surface belongs to. That point is identified with the triple $(m,n,\mathbb Z/4\mathbb{Z})$, with integers $m,n$. The $z$ class of cylinder curves lie on the cylinders that take a path from one plane to the next in our cover. Since one plane is related to exactly two others, it is impossible to go directly from the first to the third or the second to the fourth, and vice versa.

Regardless, $u$ and $v$ are the most important homology classes that we use to determine whether or not a lifted path properly closes on the four-fold cover.  Let $\alpha:[0,1]\rightarrow\mathbf M$ be a curve on the surface such that $\alpha(0)=\alpha(1)=x_0\in\mathbf{M}$. Take $f:\tilde{\mathbf U}\rightarrow\mathbf M$ to be the covering map that takes every point on $\tilde{\mathbf U}$ to its quotient in $\mathbf{M}$. We will fix a point $\tilde{x}_0\in\tilde{\mathbf U}$ such that the lifted path $\tilde\alpha(0)=\tilde{x}_0$ under the function $f$. $\alpha$ is a closed path in $\pi_1(\mathbf M,x_0)$. We denoted the class of abelianized paths $\alpha$ as [$\alpha$]$\in H_1(\tilde{\mathbf{M}},\mathbb Z)$, and define the function,

\begin{align}
i:H_1(\mathbf{M},\mathbb Z)\times H_1(\mathbf{M},\mathbb Z)\rightarrow \mathbb Z,
\end{align}

to return the intersection number of two homology classes. Out of convention, we consider a positive intersection to adhere to the right-hand rule and take the crossings to be relative to $u$ and $v$. With that being said, the signed homology classes of gamma curves are

@@

The $\mathbb{Z}^2$ cover, $\tilde{\mathbf{U}}$, is associated to the kernel of the homomorphism
\begin{align}
\Omega_{u,v}:\pi_1(\mathbf{M},x_0)\rightarrow \mathbb{Z}^2, \text{ such that } \alpha\mapsto(i(u,[\alpha]),i(v,[\alpha])).
\end{align}
Suppose that $h:\mathbf{M}\rightarrow\mathbf{M}$ is an automorphism of the surface such that dir $h\in SL(\mathbf M)$. $h$ induces the isomorphism, $h_*:\pi_1(\mathbf{M},x_0)\rightarrow \pi_1(\mathbf{M},x_0)$. Likewise, $f$ induces the inclusion map $f_*:\pi_1(\tilde{\mathbf{U}},\tilde x_0)\hookrightarrow\pi_1(\mathbf{M},x_0)$. If $\pi_1(\tilde{\mathbf{U}},\tilde x_0)$ is associated with the Ker $\Omega_{u,v}$, then it must be true that the kernel of such a homomorphism is preserved under $h_*$ and there exists a map from  $\pi_1(\mathbf M, x_0)$ to $\pi_1(\tilde{\mathbf{U}},\tilde x_0)$.

The actions of $h_*$ are dual to the actions of dir $h$, denoted $h'$, on the sets of odd-odd and even-odd $\mathbb{Z}^2$ vectors, $\mathcal{O}$ and $\mathcal{E}$. In particular, the action of $\mathbb X$ on $\mathcal{O}$ and $\mathcal{E}$ is self-contained and well-defined. This is vital as what we want to show is that $h'(\alpha')$, where $\alpha'$ is a constant and $\alpha$ is a closed geodesic, is dual to $h_*([\alpha])$. In which case, it should also be true that $h_*(\alpha)\mapsto(i(u,h_*([\alpha])),i(v,h_*([\alpha])))$, under $i$. And since intersection number is a non-degenerate bilinear form,
